Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-06-27 sattose/paper.tex
Fixed some math package problem
Better(?) type 3 equation

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{twocolpceurws}
\usepackage{float}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{tikz}
\newfloat{eqfloat}{h}{eqflts}
\floatname{eqfloat}{Equation}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

@@

\begin{eqfloat}\label{eq:type3r}
$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
$$Statements = \text{The amount of statements in this code fragment}$$
$$C_{gap} = \text{The gap between two clones}$$
$$C_{above} = \text{The clone instance above the gap}$$
$$C_{below} = \text{The clone instance below the gap}$$
\caption{Type 3R clone bridging opportunities threshold formula}\end{eqfloat}

>>>>

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{twocolpceurws}
\usepackage{float}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{amsmath,amssymb}
\usepackage{tikz}
\newfloat{eqfloat}{h}{eqflts}
\floatname{eqfloat}{Equation}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

@@

\begin{equation}\label{eq:type3r}
\text{T3R Gap}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100
\end{equation}
$$Statements = \text{Statements in a code fragment}$$
$$C_{gap} = \text{The gap between two clones}$$
$$C_{above} = \text{The clone instance above the gap}$$
$$C_{below} = \text{The clone instance below the gap}$$
